Perturbed Gait Data

### 2014-11-24 paper.tex
Update paper.tex
Edits by Ton.

  Herein we share a typical gait data set collected from 11 subjects walking at
  a three speeds on an instrumented treadmill while being longitudinally
  perturbed during each stance phase with pseudo-random fluctuations in the
  treadmill belt. We provide raw marker and ground reaction loads in addition
  to a presentation of processed data that includes gait landmarks, 2D joint
  angles, angular rates, and joint torques and the software that does the
  processing. The protocol is described in detail along with the additional
  meta data about each of the data files. This data can be useful for
  validating or generating mathematical models that capable of simulating
  non-periodic and perturbed gaits.

@@

Our motion capture system's coordinate system is such that the X coordinate
points to the right, the Y coordinate points upwards, and the Z coordinate
follows from the right-hand-rule, i.e. points backwards with respect to a
person walking forward on the treadmill. The camera's coordinate system is
aligned to an origin point on treadmill's surface during camera calibration.

@@

\begin{description}
  \item[TimeStamp] The monotonically increasing computer clock time when D-Flow
    recieves a frame from Cortex. These are approximately at 100 hz and given
    in seconds.
  \item[FrameNumber] Monotonically increasing positive integers that correspond
    to each frame received from Cortex.
  \item[Marker Coordinates] Any column that ends in \verb+.PosX+, \verb+.PosY+,
    or \verb+.PosZ+ are marker coordinates expressed in Cortex's Cartesian
    reference frame. These values are in meters.
  \item[Ground Reaction Loads] There are three ground reaction forces and three
    ground reaction moments recorded by each of the two force plates in Newtons
    and Newton-Meters, respectively. The prefix for these columns is either
    \verb+FP1+ or \verb+FP2+ and represents either force plate 1 (left) or 2
    (right). The suffixes are either \verb+.For[XYZ]+, \verb+.Mom[XYZ]+ for the
    forces and moments, respectively. The force plate voltages are sampled at a
    much higher frequency than the cameras, but delivered at the Cortex camera
    sample rate, 100 Hz through the D-Flow mocap module. A force/moment
    calibration matrix stored in Cortex converts the voltages to forces and
    moments before sending it to D-Flow [1]. Cortex also computes the center of
    pressure from the forces, moments, and force plate dimensions. These have
    the same prefixes for the plate number, have the suffix \verb+.Cop[XYZ]+,
    and are in meters.
  \item[Analog Channels] Several analog signals are recorded under column
    headers \verb+Channel[1-99].Anlg+. These correspond to analog signals
    sampled by Cortex and correspond to the 96 analog-channel National 
    Instruments 6255 DAQ box. The first twelve are the voltages from the 
    force plate load cells. We also record the acceleration of 4 points on the
    treadmill base in channels 61-72.
\end{description}

\subsection{record-xxx.txt}
%
The record module also outputs a tab delimited ASCII text file. It includes a
\verb+Time+ column which records the D-Flow system time in seconds which
corresponds to the time recorded in the \verb+TimeStamp+ column in mocap module
tsv file. There are two additional columns \verb+RightBeltSpeed+ and
\verb+LeftBeltSpeed+ which provide the independent belt speeds measure in
meters per second by an ?encoder?.

@@

We developed a command line data processing tool for common gait computations
and provide the processed data from this. The tool is centered around two main
classes, one to store a complete trial in memory and a second to compute common
gait variables of interest.

>>>>

  Herein we share a typical gait data set collected from 11 subjects walking at
  a three speeds on an instrumented treadmill while being longitudinally
  perturbed during each stance phase with pseudo-random fluctuations in the
  speed of the treadmill belt. We provide raw marker and ground reaction loads in addition
  to a presentation of processed data that includes gait landmarks, 2D joint
  angles, angular rates, and joint torques and the software that does the
  processing. The protocol is described in detail along with the additional
  meta data about each of the data files. This data can be useful for
  validating or generating mathematical models that capable of simulating
  non-periodic and perturbed gaits.

@@

Our motion capture system's coordinate system is such that the X coordinate
points to the right, the Y coordinate points upwards, and the Z coordinate
follows from the right-hand-rule, i.e. points backwards with respect to a
person walking forward on the treadmill. The camera's coordinate system is
aligned to an origin point on treadmill's surface during camera calibration.
The same point is used as the origin of the ground reaction force measuring
system.

@@

\begin{description}
  \item[TimeStamp] The monotonically increasing computer clock time when D-Flow
    recieves a frame from Cortex. These are approximately at 100 hz and given
    in seconds.
  \item[FrameNumber] Monotonically increasing positive integers that correspond
    to each frame received from Cortex.
  \item[Marker Coordinates] Any column that ends in \verb+.PosX+, \verb+.PosY+,
    or \verb+.PosZ+ are marker coordinates expressed in Cortex's Cartesian
    reference frame. These values are in meters.
  \item[Ground Reaction Loads] There are three ground reaction forces and three
    ground reaction moments recorded by each of the two force plates in Newtons
    and Newton-Meters, respectively. The prefix for these columns is either
    \verb+FP1+ or \verb+FP2+ and represents either force plate 1 (left) or 2
    (right). The suffixes are either \verb+.For[XYZ]+, \verb+.Mom[XYZ]+ for the
    forces and moments, respectively. The force plate voltages are sampled at a
    much higher frequency than the cameras, but delivered at the Cortex camera
    sample rate, 100 Hz through the D-Flow mocap module. A force/moment
    calibration matrix stored in Cortex converts the voltages to forces and
    moments before sending it to D-Flow [1]. Cortex also computes the center of
    pressure from the forces, moments, and force plate dimensions. These have
    the same prefixes for the plate number, have the suffix \verb+.Cop[XYZ]+,
    and are in meters.
  \item[Analog Channels] Several analog signals are recorded under column
    headers \verb+Channel[1-99].Anlg+. These correspond to analog signals
    sampled by Cortex and correspond to the 96 analog-channel National 
    Instruments 6255 DAQ box. The first twelve are the voltages from the 
    force plate load cells. We also record the acceleration of 4 points on the
    treadmill base in channels 61-72.  TvdB: are these useful?  If so, we need to 
    provide information on how to process these channels.  If not, maybe
    not mention them at all?
\end{description}

\subsection{record-xxx.txt}
%
The record module also outputs a tab delimited ASCII text file. It includes a
\verb+Time+ column which records the D-Flow system time in seconds which
corresponds to the time recorded in the \verb+TimeStamp+ column in mocap module
tsv file. There are two additional columns \verb+RightBeltSpeed+ and
\verb+LeftBeltSpeed+ which provide the independent belt speeds measured in
meters per second by an encoder in the treadmill.

@@

We developed a command line data processing tool for common gait computations
and provide the processed data from this. The tool was developed in Pythin and centered around two main
classes, one to store a complete trial in memory and a second to compute common
gait variables of interest.
